---
title: ""
output: html_document
---

<center>
# Sentence format / Headline / Take home message
**Analyst Name**  
*Info about analyst: title, team, company, whatever*  
`r format(Sys.Date(), '%d %B %Y')`  
</center>

```{r loadstuff, echo=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE supresses the code from showing in the report
# message=FALSE, warning=FALSE suppress messages and warnings from report

# packages you will use go here
require(ggplot2)

# data import occurs here
data(cars)

# data cleaning/manipulation, if any, goes here


```

<hr>

```{r analytics, echo=FALSE, message=FALSE, warning=FALSE}
# If you want your report to adapt to any changes in the data
# all your analysis should occur before the report starts.
# Then, you can use R objects to place soft values in the text.

# Use code chunks like this to place figures
# or use `r R_OBJECT$piece_of_object` to place object or object pieces inline

speed_stats = mean(cars$speed)

```


## Recommendations and/or Summary

- No more than about 4 *major* points or so
- Give the decision make the answer **first**
- and leave the details to further on in the report
- Average speed was `r speed_stats`  


## Important Results

These are the results that directly support the recomendation/summary.  

*Figure 1. Plot with code.*  
```{r plot1}
ggplot(cars, aes(speed, dist)) +
  geom_point() +
  geom_smooth()
```

More detail can be put in this section, rather than in recommendation/summary section.  

*Figure 2. Plot without code.*   
```{r plot2, echo=FALSE}
ggplot(cars, aes(speed, dist)) +
  geom_point() +
  geom_smooth()
```


### Dataset Features 

This section is optional, as it depends on your problem or question--writing a summary of a dataset or analysis for yourself or another data person? Use this here. Providing more of a recommendation or writing a memo for a decision maker? Move this section to the Appendix.  

Lay out missingness, outliers, reasonable assumptions/inferences, etc.  


<hr/>

## Appendices

### Methods

Write out your methods here. Include enough detail that another analyst could evaluate your approach without having to call you. 


### Assumptions / Supporting Results

This is where *Dataset Features* might go if you are writing for a decision maker. Otherwise, it can be a place to put graphs or tables or results that led to the important results, but were not in and of themselves the results.    

Things that could be included in this section might be some or all of:  

- frequencies
- ranges
- relationships
- outliers
- tables of summary stats
- missingness
- assumptions and/or assumption checks
- etc.



<hr/>

### Session Info

Providing the context that you used can be helpful if others are trying to reproduce your work.  

```{r sesinfo}
sessionInfo()
```

*~ End of file ~*
